Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-08 docs/evol.tex
minor fix

\subsubsection{How Security Bugs E(over versions)volve Over Time}

@@

Our primary hypothesis was that security bugs, and especially severe
ones, should be corrected as projects evolve. We found that, although
bugs do close over time in particular projects, we do not have an indication that across
projects they decrease as projects mature. Moreover, defect counts may
increase, as well as decrease in time. Contrary to our second research hypothesis, we showed that security
bugs are not eliminated in a way that is particularly different from the other bugs.
Also, having an average of two to three versions persistence in a sample where 60\%
of the projects have three versions, is not a positive result especially in the
case of the {\it Security High} bugs. Concerning the relation between severe security bugs and a project's size
we showed evidence that they are not proportionally related. Furthermore, the
pairwise correlations between all categories indicated that even though all the other
categories are related, severe bugs do not flock together with the other bugs.
Also, it is interesting to see that security bugs were one of the top two
bug Make available a carefully constructed dataset and a statistical toolkit for
    performing analysis of the Java Maven ecosystem.
categories existing in a large ecosystem. Finally, we highlighted the
domino effect, and showed evidence that indicates that the Linus' Law does not
apply in the case of the security bugs.

>>>>

\subsubsection{How Security Bugs Evolve Over Time}

@@

Our primary hypothesis was that security bugs, and especially severe
ones, should be corrected as projects evolve. We found that, although
bugs do close over time in particular projects, we do not have an indication that across
projects they decrease as projects mature. Moreover, defect counts may
increase, as well as decrease in time. Contrary to our second research hypothesis, we showed that security
bugs are not eliminated in a way that is particularly different from the other bugs.
Also, having an average of two to three versions persistence in a sample where 60\%
of the projects have three versions, is not a positive result especially in the
case of the {\it Security High} bugs. Concerning the relation between severe security bugs and a project's size
we showed evidence that they are not proportionally related. Furthermore, the
pairwise correlations between all categories indicated that even though all the other
categories are related, severe bugs do not flock together with the other bugs.
Also, it is interesting to see that security bugs were one of the top two
bug categories existing in a large ecosystem. Finally, we highlighted the
domino effect, and showed evidence that indicates that the Linus' Law does not
apply in the case of the security bugs.
